A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-03-12 pilot-publication/manuscript.Rmd
Correct meeting date
Add meeting notes reference

### Sequence generation
We used simple randomisation to allocate sites to trial arms. We
prepared seven sealed envelopes from which one representative from
each pilot site selected one in a common meeting on March 8, 2022
[^dev1]. The content of the envelopes dictated what trial arm (ATLS,
PTC, or standard care) each hospital was allocated to. There were two
hospitals in each of the intervention arms and three hospitals in the
control arm.

>>>>

### Sequence generation
We used simple randomisation to allocate sites to trial arms. We
prepared seven sealed envelopes from which one representative from
each pilot site selected one in a common meeting on March 7, 2022
[^dev1]<!-- Meeting notes ../meetings/20220307/ -->. The content of
the envelopes dictated what trial arm (ATLS, PTC, or standard care)
each hospital was allocated to. There were two hospitals in each of
the intervention arms and three hospitals in the control arm.
